%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Queue Management System} % Job title
    {QMagik} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Involved in Analysis and Design Phase.}
        \item {Playing a major role in android app development.}
        \item {Working with backend team to implement features in android app.}
        \item{http://www.qmagik.com/}
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {Appointment management system for consulting doctors} % Job title
    {AsterApps} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactored application.}
        \item{https://play.google.com/store/apps/details?id=com.dieutek.volkermotor}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {ERP suite specially designed for Latex based product manufacturing industry} % Job title
    {gerp+ } % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Involved in Analysis and Design Phase.}
        \item {Played a major role in android app development.}
        \item {Released Application in Google Play.}
        \item{http://www.thegti.com/Content.aspx?CV=7}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Service booking application with features like Insurance remainder, Service remainder} % Job title
    {Volker Motors} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Involved in Analysis and Design Phase.}
        \item {Developed the whole app.}
        \item {Implemented server application using JSON-REST services.}
        \item {Published Application on Google Play.}
        \item{https://play.google.com/store/apps/details?id=com.dieutek.volkermotor}
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {2D game with flight of a bird as the main perspective} % Job title
    {KoKo Fly} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develped using Unity 5.1.2}
        \item {Published Application on Google Play.}
        \item{https://play.google.com/store/apps/details?id=com.Dieutek.kokofly}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
